A fully labelled proof system for intuitionistic modal logics

### 2019-10-08 caleidoscope/introduction.tex
added missing fresh labels on proofs

Besides that, there is another pleasant observation to make about our
system. Ordinary labelled sequent systems for intuitionistic modal
logic are single-conclusion~\cite{simpson:phd}. 
\sonia{No! the system for epistemic logic by Maffezioli, Naibo and Negri~\cite{maffezioli:etal:synthese13} is multi-conclusion}
\todo{need to say that it is the same principle as in their work, but we use in a more general setting and extend it to a framework for many intuitionistic modal logics while keeping the nice invertibility property.}
%
The same is true for the corresponding nested sequent
systems~\cite{str:fossacs13,marin:str:aiml}. It is possible to express
Maehara style multiple-conclusion systems in nested
sequents~\cite{kuz:str:maehara}, and therefore also in ordinary
labelled sequents. However, also in these systems there are rules
($\rlabrn\IMP$ and $\rlabrn\BOX$) that force a single-conclusion
premise, even though this is not the case in labelled
systems~\cite{negri:jpl2005} or nested sequents~\cite{fitting:83} for
intuitionistic logic. Our system eliminates this
discrepancy. Consequently, every rule in our system is invertible, as
we never delete information.

>>>>

Besides that, there is another pleasant observation to make about our
system. Ordinary labelled sequent systems for intuitionistic modal
logic are single-conclusion~\cite{simpson:phd}. 
\sonia{No! the system for epistemic logic by Maffezioli, Naibo and Negri~\cite{maffezioli:etal:synthese13} is multi-conclusion}
\todo{need to say that it is the same principle as in their work, but we use in a more general setting and extend it to a framework for many intuitionistic modal logics while keeping the nice invertibility property.}
%
The same is true for the corresponding nested sequent
systems~\cite{str:fossacs13,marin:str:aiml}. It is possible to express
Maehara style multiple-conclusion systems in nested
sequents~\cite{str:2017maehara}, and therefore also in ordinary
labelled sequents. However, also in these systems there are rules
($\rlabrn\IMP$ and $\rlabrn\BOX$) that force a single-conclusion
premise, even though this is not the case in labelled
systems~\cite{negri:jpl2005} or nested sequents~\cite{fitting:83} for
intuitionistic logic. Our system eliminates this
discrepancy. Consequently, every rule in our system is invertible, as
we never delete information.
